|

### 2021-09-16 paper.Rmd
back on track

<!-- % still, we know little about the role of discrete emotions in interacting with misinformation and corrective information -->
While this has been linked to affect [@thorson2016belief], the connection of distinct emotions to both susceptibility to misinformation, and the effectiveness of corrective information is under-explored. This is unfortunate given the important role that emotional appeals play in the dissemination of false or misleading information. We know that false news spread faster than true news, possibly because they are more likely to evoke emotions of surprise and disgust [@vosoughi2018spread]. In general, moral-emotional language is rewarded on social media [@brady2017emotion].
<!-- and populist parties use more negative emotional appeals in their communication than non-populist parties [@widmann2021how]. -->

>>>>

<!-- % still, we know little about the role of discrete emotions in interacting with misinformation and corrective information -->

While this has been linked to affect [@thorson2016belief], the connection of distinct emotions to both susceptibility to misinformation, and the effectiveness of corrective information is under-explored. This is unfortunate given the important role that emotional appeals play in the dissemination of false or misleading information. We know that false news spread faster than true news, possibly because they are more likely to evoke emotions of surprise and disgust [@vosoughi2018spread]. In general, moral-emotional language is rewarded on social media [@brady2017emotion].
